The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-04-25 paper/ms.tex
Add circular guiding orbit earlier

\subsection{Epicyclic Approximation} \label{ssec:epi_action}
Before turning to numerical methods, we first write down analytically the systematic error in the actions induced from either a midplane offset or a Galactocentric radius
offset. We use the epicyclic approximation, which assumes that the motion in
the $z$ and $R$ components of the orbit are decoupled and follow simple
harmonic motion \citep[][section 3.2 and references therein]{2008gady.book.....B}. This approximation is an excellent description of
thin disk-like orbits, and a good description of thick disk-like orbits, in an axisymmetric potential (i.e. ignoring the influence of the Galactic bar and spiral arms). We
also make the assumption of a perfectly flat circular velocity curve with
velocity $v_c$ \citep[decent near the Solar circle, e.g.][]{2017MNRAS.465...76M}.

@@

We can write down the actions in this approximation as
\citep[][Section~3.5.3b]{2008gady.book.....B},
\beq\label{eq:actions_epi}
\begin{split}
J_{\phi} &= R_g v_c \\
J_R &= \kappa A_R^2 \\
J_z &= \nu A_z^2\text{,}
\end{split}
\eeq
where $R_g$ is the guiding radius of the orbit.

>>>>

\subsection{Epicyclic Approximation} \label{ssec:epi_action}
Before turning to numerical methods, we first write down analytically the systematic error in the actions induced from either a midplane offset or a Galactocentric radius
offset. We use the epicyclic approximation, which assumes that the motion in
the $z$ and $R$ components of the orbit are decoupled and follow simple
harmonic motion about a circular and planar ``guiding orbit'' \citep[][Section 3.2 and references therein]{2008gady.book.....B}. We refer to the radius of this orbit (the ``guiding radius'') as $R_g$. This approximation is an excellent description of
thin disk-like orbits and a good description of thick disk-like orbits in an axisymmetric potential (i.e. ignoring the influence of the Galactic bar and spiral arms). We
also make the assumption of a perfectly flat circular velocity curve with
velocity $v_c$ \citep[decent near the Solar circle, e.g.][]{2017MNRAS.465...76M}.

@@

We can write down the actions in this approximation as
\citep[][Section~3.5.3b]{2008gady.book.....B},
\beq\label{eq:actions_epi}
\begin{split}
J_{\phi} &= R_g v_c \\
J_R &= \kappa A_R^2 \\
J_z &= \nu A_z^2\text{.}
\end{split}
\eeq
